\chapter{IPA apartment rules}\label{chap:apartment-rules}


%##########################################################
%##########################################################
\section{Working in the robot area}
The robot area is considered the left side of the room after entering from the main door.

%##########################################################
\subsection{Using pool pcs}
The pool pcs have a fixed configuration and the installed packages should all be the same on all machines. If you need an account, a new installation of packages or software in the pcs please contact \href{mailto:nhg@ipa.fhg.de}{nhg@ipa.fhg.de} or \href{mailto:fmw@ipa.fhg.de}{fmw@ipa.fhg.de}.

\subsubsection{Don't change any cabling}\label{sec:cabling}
You should not add, remove or change any cabling. Especially all cables below the tables should not be touched at all because they are ordered in a way that power distribution and network distribution is optimized. Cabling includes power, network, monitors, keyboards and mouse. If you feel the need for changing anything, please contact \href{mailto:fmw@ipa.fhg.de}{fmw@ipa.fhg.de} or \href{mailto:nhg@ipa.fhg.de}{nhg@ipa.fhg.de}.

\subsubsection{Don't turn off the pcs}\label{sec:poolpcs}
The pcs are used remotely during daytime, the night and the weekend, so please just log out and don't turn them off.

%##########################################################
\subsection{Using your own pc}
You can use your own pc and connect to the network. Using the network plugs you should get an IP address over DHCP and connect to the internet.

\subsubsection{Don't use the plugs under the tables}
See section \ref{sec:cabling}

\subsubsection{Use the plugs on the tables}
If you want to connect to power or network use the power and network plugs on the table. You can find additional power and network cables in cabinet III, see section \ref{sec:floorplan}. Please put them back when you leave the room.

\subsubsection{Don't disconnect to the pool pc monitors, mouse and keyboard}
If you need a monitor, mouse or keyboard for your laptop, please use the ones out of cabinet III, see section \ref{sec:floorplan}. Don't disconnect one of the pool pc monitors.

%##########################################################
\subsection{Leaving the robot area}
\subsubsection{Move all furniture back}
Please move all tables, chairs and cupboards back to their default place. The default place for all objects can be found in the floor plan of section \ref{sec:floorplan}.

\subsubsection{Tidy up working places}\label{sec:tidyup}
Please remove everything from the tables of cob-stud-6 to cob-stud-9. There should be nothing left on the tables except monitors, keyboard, mouse and telephone. Remove everything else, like coffee cups, bottles, paper, ...

\subsubsection{Unplug additional network and power cables}
Please unplug everything you plunged in on the tables and put the cables back to cabinet III, see section \ref{sec:floorplan}.

\subsubsection{Logout your user from pool pcs}
After finishing your work please log off so that other users can use the pc. You should not login in into two machines at the same time to avoid problems.

\subsubsection{Turn off the monitors}\label{sec:monitor}
To safe energy please turn off the monitor after using it but keep the pool pcs on, see section \ref{sec:poolpcs}.


%##########################################################
%##########################################################
\section{Working on the student side}
The student side is considered the right side of the room behind the cupboards after entering from the main door.

%##########################################################
\subsection{Leaving your work place}

\subsubsection{Don't turn off the pc}
See section \ref{sec:poolpcs}.

\subsubsection{Turn off your monitor}
See section \ref{sec:monitor}.

\subsubsection{Tidy up working places}
See section \ref{sec:tidyup}. Use your student storage shelf to store your personal belongings.

%##########################################################
\subsection{Leaving the room as the last person}
If nobody else is in the room any more, which means robot and student side, please follow the following additional rules. You are probably the last one if you leave later than 6pm in the evening.

\subsubsection{Close the windows}
Please close all windows on both sides of the room.

\subsubsection{Turn off the lights}
Turn off all lights on both sides of the room.

%##########################################################
%##########################################################
\section{Floor plan}\label{sec:floorplan}
TODO: add floor plan for robot area and student side